Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-12-01 Ben_Manuscripts/structure_paper/Outline.tex
comments on outline
Updated with better organization and some new figures

   \item Is it necessary to include any water in order to appropriately model the 
   Col\textsubscript{h} phase? \label{point:water}
   \begin{itemize}
	\item While the Col\textsubscript{h} phase is described as dry, it is 
	possible that small amounts of ambient water may be leached into the system.
	\item The hydrogen bonding network formed by the water may play a role 
        in structuring the pore.
	\item We can use simulated X-ray diffraction patterns to see if there is
        any meaningful structural difference between a "dry" and "wet" system
   \end{itemize}
    \end{enumerate}
%MRS2: size and how well defined the pore is (how suddenly the RDF changes in the pore) is also a question.

%MRS2: hmm.  This last point still seems somewhat relevant.  Why left out?
%BJC: I thought we agreed to leave this out. It lengthens the paper and makes it
% more confusing. Unless we just want to hint at it.

%     \item While we might be able to provide answers to these questions using a 
%     molecular model, there remains the possibility that there is more than one 
%     metastable state associated with a given LLC system.

%  (4) Can the system exist in other metastable states or phases that are not
%  accessed during experiments?
%  There remains the possibility that there is more than one metastable state 
%  associated with a given LLC system.
%  \begin{itemize}
%    \item Simulating a membrane atomistically will require many atoms which further
%    limits the timescales acessible with MD
%    \item It is reasonable to expect that we will generate configurations which 
%    are kinetically trapped in a metastable free energy basin
%    \item We must be able to identify which state is produced experimentally and 
%    why others are not.
%  \end{itemize}

  %Once we have addressed all of the above questions, we must show that the 
  %developed molecular model is consistent with physical observations so that we
  %can rely on conclusions drawn about structural features characteristic of 
  %the system.
  In this study, we build a significantly more realistic atomistic model of LLC membranes
  than has ever previously been done, and explore what new structural information can be gained
  and what structure hypotheses are supported by this model.

  \begin{itemize}
    \item We validate the model using as much experimental information as possible.
    \item We are most interested in reproducing the conclusions about structure
    which have been made from X-ray diffraction (XRD) experiments and in matching ionic
    conductivity measurements~\cite{feng_thin_2016}.
    \begin{itemize}
	    \item We have compared simulated X-ray diffraction patterns to experiment in 
	    order to match major features present in the 2D patterns.
	    \item We calculated ionic conductivity using two agreeing methods.
	    \item We examined the the influence of crosslinking on membrane structure.
    \end{itemize}
    \item The structure-building approach and analysis used in this paper can be readily extended
    to the H\textsubscript{II} phase, other similar LC systems and ultimately to help design
    real membranes.
  \end{itemize}

@@

@@

@@

  A typical simulation volume contains four pores in a monoclinic unit cell,
  the smallest unit cell that maintains hexagonal symmetry when extended 
  periodically.
  \begin{itemize}
    \item Each pore is made of twenty stacked monomer layers with periodic 
    continuity in the z direction, avoiding any edge effects and creating an 
    infinite length pore ideal for studying transport.
    \item Each layer is made of a set number of monomers per layer, a variable to
    be explored further.
    \item A small number of layers is preferred in order to reduce computational
    cost and to allow us to look at longer timescales.
    \item Ultimately, we chose to build a system with 20 monomer layers in each pore
    in order to obtain sufficient resolution when simulating X-ray diffraction patterns.
    This point will be explained in more detail later.
    %MRS: you should give the reasons in the same place you describe the choice, but the supporting data would probably be better in supporting information
    %BJC: so refer to supporting info here? Then put plots of diffraction data with different sized system there. I did not explain the resolution point here because I haven't talked about simulated X-ray diffraction yet and it wouldn't make sense. And it doesn't make sense to talk about XRD this early in the methods but I need to justify the number of layers.
    %MRS2: I was referring to the data choice of 20 vs 10.  Yes, you can refer to it here, because the expectation is that peple will only look at it after reading the whole paper.
    \item We chose initial guesses for the remaining structural parameters based on
    experimental data and treated them as variables during model development.
  \end{itemize}

@@

%MRS2: make it clear these choices are for INITIAL spacing, and that this adjusted based on MD.  Also want to make
%sure the dependence of the initial choices is described in supporting information, as the results shouldn't be TOO dependnt on thesechoices.
%BJC: okay will work on some figures illustrating the affect of initial choices on results
  We chose the layer spacing for the initial configuration based on R-$\pi$ and then allowed system
  to readjust during equilibration.
  \begin{itemize}  
    \item Each monomer was rotated so the plane of the aromatic head groups would
    be parallel to the xy plane.
%MRS2: seems like the choice of separation distance here should be detailed in the supporting information, and how it changes  the structures formed.  Also, not quite clear. 
%BJC: okay, I have some ideas for this
    \item The layers are placed so aromatic rings are stacked 3.7 \angstrom~
    apart in the z-direction.
    \item To quantify the degree of layering in our system, we calculated
    a spatial correlation function, $g(z)$, measured along the z-axis 
    (perpendicular to the membrane plane)
    \item To calculate $g(z)$, we binned the z component distances between 
    the center of mass of each benzene ring and all others of the same pore 
    over 50 ns of equilibrated trajectory and then normalized by the average
    number density.
    \item We compare the degree of layering between systems based on the
    amplitude of the first peak in $g(z)$. We halve the difference between the
    maximum of the first peak and the following minimum. We compare the difference
    to the mean to get a percentage deviation from the average number density.
    \item To extract the average distance between layers we applied a discrete 
    fourier transform to $g(z)$ and extracted the highest intensity frequency 
  \end{itemize}

  We placed pores at a chosen initial spacing based on R-pores, then allowed
  the system to settle into its preferred spacing. 
  \begin{itemize}
    %MRS: somewhere, should explain there's a large dependence of (meta)stable structures based on this initial distance.  It's sort of important to put somewhere.
    %BJC: Sure, but different choices of pore spacing were based on number of monomers per layer. More monomers per layer means a larger initial pore spacing.
    \item The model's pore centers are spaced 4.5 nm apart initially, $\approx$ 10 \% larger
    than the experimental value of 4.12 nm in order to reduce unintended repulsions 
    resulting from a tightly packed initial configuration.
    \item To calculate the equilibrated pore spacing, we measured the distance between pore
    centers.
    \item Pore centers were located by averaging the coordinates of sodium ions in their 
    respective pores.
    \item Statistics were generated using the bootstrapping technique (See Supplemental Information)
    	% Supplemental vvvv
	\begin{itemize}
        %MRS2: make clear sampling what?
        \item We are interested in 5 pore-to-pore distances which should all be equal in
        a perfect hexagonal array, however only 4 distances are independent % can visualize this in supplemental material. Will make a lot of things more clear below.
	\item Each pore spacing has its own trajectory of spacing vs. time. Using data collected after
	the system is equilibrated, we calculate how long it takes for the data in each of the 5
	trajetories to become uncorrelated using pymbar.timeseries.integratedAutocorrelationTime() % reference
	\item We break the full trajectories down into sub-trajectories based on the
	maximum autocorrelation time of those found in the previous step. 
    	\item For each bootstrap trial, we recreate an equilibrium trajectory by randomly 
    	sampling pore spacings from the sub-trajectories 
    	\item We get an average value for each pore spacing by finding the mean of the bootstrapped data
	\item We calculate the overall average as the mean of all bootstrapped pore spacings
	\item The uncertainty for each pore spacing is calculated as $\dfrac{<x> - x}{4}$ where $<x>$ is the
	average spacing from the bootstrap trial and $x$ is the average value of one of the pore spacings.
	\item We report the mean of these uncertainties
        % MRS: need to deal with the fact only 4 are independent in the bootstrapping?  How did we do that?
	% BJC: Updated
        % Supplemental ^^^^
	\end{itemize}
  \end{itemize}

  %MRS: pore radius is a different category isn't it? Is this an input piece of data?
  % should be put in a different category.
  %BJC: Well I still have to initially place the monomers some distance away from the pore
  % centers. That distance is informed by the experimental evidence.

%  We based the pore radii of our initial configuration on past TEM and size exclusion 
%  rejection data
%MRS2: maybe this fits somewhere else, since it's not really used in the same way - it's more descriptive.  In fact, maybe better to say it WASN'T used at all to constrain initial choice, and we simply looked at it after to understand how the pore size is affected by other choices.  Or maybe I'm still misunderstanding.

  We used experimental Transmission electron microscopy (TEM) and size exclusion rejection
  data \cite{feng_scalable_2014,feng_thin_2016,zhou_supported_2005} to inform our definition
  of pore radius in the initial configuration.
  \begin{itemize}
    \item Experimental evidence suggests uniform pores with radii of 0.6 nm 
    \item Comparing a geometric measurement of pore size derived from an atomistic model,
    to a less precise, experimentally derived pore size estimate, will give ambiguous results.
    \item What is meant by pore radius will not be clear until we establish a clear picture
    of the nanoscopic pore environment.
    \item When constructing pores, we chose the carboxylate carbon from the monomer
    head group as a reference atom, and placed it a distance r from the pore center,
    where r is the pore radius (~\ref{fig:pore_radius_illustration}). % BJC: Figure in Supplemental Information?
    \item We will not make direct comparisons of pore radius between our model 
    and experiment to avoid the ambiguity, however, we do define a pore radius  
    for our own purposes.
    %\item To measure the pore radius in our model we calculate the distance between 
    %the center of mass of each aromatic ring and the center of mass of all aromatic rings
    %in their respective pores.
  \end{itemize}

%MRS2: is the pore radius of the initial configuration really relevant? Does it need to be defined?  Seems like what radius means in the final equilibrated one is more important.
%BJC: maybe not, we'll have to talk to get on the same page
  \begin{figure}
 	\centering
 	\includegraphics[width=\textwidth]{pore_radius_illustration.png}
	\caption{The pore radius of the initial configuration is defined using the 
        carboxylate carbon as a reference}~\label{fig:pore_radius_illustration}
  \end{figure}

  The relative interlayer orientation was chosen based on clues from 
  diffraction data as well as the various known stacking modes of benzene 
  and substituted benzene rings: sandwiched, parallel-displaced and T-shaped
  ~\cite{sinnokrot_estimates_2002} (\Cref{fig:sandwiched,fig:pd,fig:tshaped}).
  \begin{itemize}
    \item The T-shaped configuration was ruled out based on the inconsistency of
    its $\approx$ 5 \angstrom~equilibrium stacking distance ~\cite{sinnokrot_estimates_2002}.
    \item The system's preference towards the sandwiched vs. parallel displaced 
    stacking modes will be explored.
    \item Both have reported stacking distances near the R-$\pi$ value of 3.7 \angstrom % Reference
    \item Headgroups in the sandwiched configuration are stacked directly on top of
    each other while stacked headgroups in the parallel displaced configuration are offset 
    by $180/nmon$ degrees where $nmon$ equals the number of monomers per layer.
    %BJC: I think the following commentary belongs elsewhere, maybe even in the discussion
    %MRS: hard to say. It's certainly a big switch from things that are relatively straightforward to things that require 
    % a fair amount of information, so I think it belongs in it's own section -- so far, you're just laying out the approach.  This is what we fix, this is what we leave as a variable.  The analysis probably belongs later.
    %BJC: Yeah, I will leave the rest for discussion
%     \item Visualization of each configuration (\Cref{fig:sandwichedlayers,fig:offsetlayers})
%     suggests entropic differences based on the way the tails are able to pack.
%     \item In the sandwiched configuration, all tails start out directly on top
%     of each other which may prevent closely stacked benzene rings.
%     \item In the offset configuration, the tails are placed in between each other 
%     which may allow layers to come together in a compact way.
%     \item This difference may explain, in part, which stacking mode is more favorable.
  \end{itemize}

%MRS2: seems like the number per layer might be listed here, since that was adjusted during the fitting process?  Hmm.  I see it's later in the results. It's a bit confusing what variables are listed here (initial geometry settings), and what is discussed in the results section. (like number per layer)  We should discuss.

  %We tested a number of equilibration schemes of increasing complexity in an effort
  %to match experiment while overcoming kinetic limitations that might trap the system 
  %in a metastable states. All start from an initial configuration generated with 
  %chosen structure variables.
  We developed equilibration schemes to create dry and wet configurations. Both schemes 
  start with an initial configuration generated according to the previous guidelines.
  \begin{itemize}
      \item Dry equilibration scheme:
      \begin{itemize}
        %MRS2: what initial force constant, and does it matter (that can be in supplemental) 
	%BJC: I've never explored whether there is any dependence on initial force constant. It probably doesn't matter unless it starts really low
          \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
          configurations while allowing monomer tails to settle.
          \item Doing so also mitigates system dependence on initial monomer configuration.
          \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
          \item Every 50 ps, we reduce the force constants by the square root of its
          previous value, starting from 1e6 KJ mol$^-1$ nm$^-2$.
          \item Once the force constant is below 10 KJ mol$^-1$ nm$^-2$, the restraints are
          released linearly until there is no more restraining potential.
          \item The resulting unrestrained structure is allowed to equilibrate for 5 ns 
	  in the NPT ensemble with pressure controlled by the berendsen barostat.
	  \item Long, NPT equilibration simulations are run for at least 400 ns using the 
          Parrinello-Rahman barostat with a time consant of 10 ps.
      \end{itemize}
      \item Wet equilibration scheme: 
      \begin{itemize}
	  % BJC: the following three bullet points ended up not being the case since I used significantly less water
          %\item We obtained an estimate of equilibrium pore water content by solvating
          % an initial configuration with water baths above and below the membrane. 
	  %\item We ran the solvated system according to Scheme A but with a 1000 ns equilibration
          %\item Using that number we added water to the pores of an initial 
	  %configuration and equilibrated according to scheme B. 
	  \item In order to create a wet system, we solvated an initial configuration with water using gmx solvate
          \item All waters placed outside the pore region are removed 
	  \item Waters inside the pore region are randomly removed until the desired concentration
	  of water in the pores is reached. 
	  \item The remainder of the equilibration is the same as the dry system
      \end{itemize}
      \item In all cases, the v-rescale thermostat was used with tau-t = 0.1 % BJC: supplemental
  \end{itemize}

@@

@@

  \begin{figure}
	\centering
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwiched.png}
		\caption{}\label{fig:sandwiched}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{PD.png}
		\caption{}\label{fig:pd}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Tshaped.png}
		\caption{}\label{fig:tshaped}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwichedlayers.png}
		\caption{}\label{fig:sandwichedlayers}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offsetlayers.png}
		\caption{}\label{fig:offsetlayers}
	\end{subfigure}
	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
	3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart. 
	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
	configuration }\label{fig:stacking}
  \end{figure}

>>>>

  \item Can the system exist in other metastable states or phases that are not
  accessed during experiments? \label{point:metastable}
  There remains the possibility that there is more than one metastable state 
  associated with a given LLC system.
  \begin{itemize}
    \item Simulating a membrane atomistically will require many atoms which further
    limits the timescales acessible with MD
    \item It is reasonable to expect that we will generate configurations which 
    are kinetically trapped in a metastable free energy basin
    \item We must be able to identify which state is produced experimentally and 
    why others are not.
  \end{itemize}

  \item What constitutes a pore and how well-defined are the pore regions? \label{point:poredefinition}
  \begin{itemize}
	\item The limited picture that experiment provides tells us that there are
        hexagonally packed, hydrophilic regions where transport is likely to occur
	\item One may instinctively assume that these regions are tube-like pathways
	\item We will explore the composition of the pores and the partition
	between the hydrophilic and hydrophobic regions. 
  \end{itemize}

  \item Is it necessary to include any water in order to appropriately model the 
  Col\textsubscript{h} phase? \label{point:water}
  \begin{itemize}
	\item While the Col\textsubscript{h} phase is described as dry, it is 
	possible that small amounts of ambient water may be leached into the system.
	\item The hydrogen bonding network formed by the water may play a role 
        in structuring the pore.
	\item We can use simulated X-ray diffraction patterns to see if there is
        any meaningful structural difference between a "dry" and "wet" system
  \end{itemize}
  \end{enumerate}

  %Once we have addressed all of the above questions, we must show that the 
  %developed molecular model is consistent with physical observations so that we
  %can rely on conclusions drawn about structural features characteristic of 
  %the system.

  In this study, we build a significantly more realistic atomistic model of LLC membranes
  than has ever previously been done, and explore what new structural information can be gained
  and what structure hypotheses are supported by this model.

  \begin{itemize}
    \item We validate the model using as much experimental information as possible.
    \item We are most interested in reproducing the conclusions about structure
    which have been made from X-ray diffraction (XRD) experiments and in matching ionic
    conductivity measurements~\cite{feng_thin_2016}.
  \end{itemize}

%    \begin{itemize}
%            \item We have compared simulated X-ray diffraction patterns to experiment in
%            order to match major features present in the 2D patterns.
%            \item We calculated ionic conductivity using two agreeing methods.
%            \item We examined the the influence of crosslinking on membrane structure.
%    \end{itemize}
%    \item The structure-building approach and analysis used in this paper can be readily extended
%    to the H\textsubscript{II} phase, other similar LC systems and ultimately to help design
%    real membranes.
%  \end{itemize}

@@

  %BJC: The Methods sections has four main topics which will be separated by an appropriate header

  %%%%%%%%% Monomer Preparation %%%%%%%%%%%%%

@@

  %%%%%%%% UnitCell Preparation %%%%%%%%%%%%%

@@

  A typical simulation volume contains four pores in a monoclinic unit cell,
  the smallest unit cell that maintains hexagonal symmetry when extended 
  periodically.
  \begin{itemize}
    \item Each pore is made of twenty stacked monomer layers with periodic 
    continuity in the z direction, avoiding any edge effects and creating an 
    infinite length pore ideal for studying transport.
%    \item Each layer is made of a set number of monomers per layer, a variable to
%    be explored further.
    \item A small number of layers is preferred in order to reduce computational
    cost and to allow us to look at longer timescales.
    \item Ultimately, we chose to build a system with 20 monomer layers in each pore
    in order to obtain sufficient resolution when simulating X-ray diffraction patterns.
    This point will be explained in more detail later.
    %MRS: you should give the reasons in the same place you describe the choice, but the supporting data would probably be better in supporting information
    %BJC: so refer to supporting info here? Then put plots of diffraction data with different sized system there. I did not explain the resolution point here because I haven't talked about simulated X-ray diffraction yet and it wouldn't make sense. And it doesn't make sense to talk about XRD this early in the methods but I need to justify the number of layers.
    %MRS2: I was referring to the data choice of 20 vs 10.  Yes, you can refer to it here, because the expectation is that peple will only look at it after reading the whole paper.
%    \item We chose initial guesses for the remaining structural parameters based on
%    experimental data and treated them as variables during model development.
  \end{itemize}

@@

  %%%%%%%%%%%% Monomer Placement %%%%%%%%%%%%%%

  When constructing an initial configuration, there are a number of variables
  which require careful consideration while placing monomers. The equilibrium
  configuration is sensitive to some while insensitive to others.
  \begin{itemize}
	\item The starting pore radius, defined as the distance of a chosen 
        head group carbon from the pore's central axis, does not influence the
        equilibrium structure when a reasonable value is chosen (See Supplemental)
        \item The pore radius is chosen to be 0.6 nm in our initial configurations 
        because the pore size is estimated to be $\approx$ 1.2 nm % Add reference
	\item The initial distance between pores also has little effect on the 
        the equilibrated structure. However, one should not start them too close or there 
        will likely be unintended high energy repulsions during early equilibration
	\item We chose an initial pore spacing of 4.5 nm, $\approx$ 10 \% larger than 
        the experimental value of 4.12 nm.
        \item The distance between layers and the rotation of the layers with respect
        to adjacent layers, and the number of monomers per layer do influence the 
        equilibrium structure and require further justification for their choices. 
        \item We rely on experimental data to inform our choices
  \end{itemize}

  We chose the layer spacing for the initial configuration based on R-$\pi$ 
  and then allowed system to readjust during equilibration.
  \begin{itemize}  
    \item Each monomer was rotated so the plane of the aromatic head groups would
    be coplanar with the xy plane.
    \item We explore two different initial layer spacings
    \item The first is exactly equal to R-$\pi$ with layers placed so aromatic
    rings are stacked 3.7 \angstrom~ apart in the z-direction.
    \item A second system is explored with an initial layer spacing of 5 \angstrom
    \item A third system with an initial layer spacing of 10 \angstrom was briefly
    explored and the reader can learn more about it in the Supplemental Information.
% BJC: Move all this lower down to be with the rest of the equilibrium calculations
%    \item To quantify the degree of layering in our system, we calculated
%    a spatial correlation function, $g(z)$, measured along the z-axis 
%    (perpendicular to the membrane plane)
%    \item To calculate $g(z)$, we binned the z component distances between 
%    the center of mass of each benzene ring and all others of the same pore 
%    over 50 ns of equilibrated trajectory and then normalized by the average
%    number density.
%    \item We compare the degree of layering between systems based on the
%    amplitude of the first peak in $g(z)$. We halve the difference between the
%    maximum of the first peak and the following minimum. We compare the difference
%    to the mean to get a percentage deviation from the average number density.
%    \item To extract the average distance between layers we applied a discrete 
%    fourier transform to $g(z)$ and extracted the highest intensity frequency 
  \end{itemize}

% BJC: removing this since I say earlier that the system is insensitive to this choice
% Detail will be provided in the supplement
% discussion of measuring equilibrium pore spacing is moved down to calculations part of methods
%  We placed pores at a chosen initial spacing based on R-pores, then allowed
%  the system to settle into its preferred spacing. 
%  \begin{itemize}
    %MRS: somewhere, should explain there's a large dependence of (meta)stable structures based on this initial distance.  It's sort of important to put somewhere.
    %BJC: Sure, but different choices of pore spacing were based on number of monomers per layer. More monomers per layer means a larger initial pore spacing.
%    \item The model's pore centers are spaced 4.5 nm apart initially, $\approx$ 10 \% larger
%    than the experimental value of 4.12 nm in order to reduce unintended repulsions 
%    resulting from a tightly packed initial configuration.
%    \item To calculate the equilibrated pore spacing, we measured the distance between pore
%    centers.
%    \item Pore centers were located by averaging the coordinates of sodium ions in their 
%    respective pores.
%    \item Statistics were generated using the bootstrapping technique (See Supplemental Information)
    	% Supplemental vvvv
%	\begin{itemize}
        %MRS2: make clear sampling what?
%        \item We are interested in 5 pore-to-pore distances which should all be equal in
%        a perfect hexagonal array, however only 4 distances are independent % can visualize this in supplemental material. Will make a lot of things more clear below.
%	\item Each pore spacing has its own trajectory of spacing vs. time. Using data collected after
%	the system is equilibrated, we calculate how long it takes for the data in each of the 5
%	trajetories to become uncorrelated using pymbar.timeseries.integratedAutocorrelationTime() % reference
%	\item We break the full trajectories down into sub-trajectories based on the
%	maximum autocorrelation time of those found in the previous step. 
%    	\item For each bootstrap trial, we recreate an equilibrium trajectory by randomly 
%    	sampling pore spacings from the sub-trajectories 
%    	\item We get an average value for each pore spacing by finding the mean of the bootstrapped data
%	\item We calculate the overall average as the mean of all bootstrapped pore spacings
%	\item The uncertainty for each pore spacing is calculated as $\dfrac{<x> - x}{4}$ where $<x>$ is the
%	average spacing from the bootstrap trial and $x$ is the average value of one of the pore spacings.
%	\item We report the mean of these uncertainties
        % MRS: need to deal with the fact only 4 are independent in the bootstrapping?  How did we do that?
	% BJC: Updated
        % Supplemental ^^^^
%	\end{itemize}
%  \end{itemize}

% BJC: This can be covered more in the Supplmental ... it might not even be necessary. I won't
% report any "pore sizes" except in the supplemental where I will show that the initial choice
% of pore radius has little effect on pore size

%  We used experimental Transmission electron microscopy (TEM) and size exclusion rejection
%  data \cite{feng_scalable_2014,feng_thin_2016,zhou_supported_2005} to inform our definition
%  of pore radius in the initial configuration.
%  \begin{itemize}
%    \item Experimental evidence suggests uniform pores with radii of 0.6 nm 
%    \item Comparing a geometric measurement of pore size derived from an atomistic model,
%    to a less precise, experimentally derived pore size estimate, will give ambiguous results.
%    \item What is meant by pore radius will not be clear until we establish a clear picture
%    of the nanoscopic pore environment.
%    \item When constructing pores, we chose the carboxylate carbon from the monomer
%    head group as a reference atom, and placed it a distance r from the pore center,
%    where r is the pore radius (~\ref{fig:pore_radius_illustration}). % BJC: Figure in Supplemental Information?
%    \item We will not make direct comparisons of pore radius between our model 
%    and experiment to avoid the ambiguity, however, we do define a pore radius  
%    for our own purposes.
    %\item To measure the pore radius in our model we calculate the distance between 
    %the center of mass of each aromatic ring and the center of mass of all aromatic rings
    %in their respective pores.
%  \end{itemize}

%MRS2: is the pore radius of the initial configuration really relevant? Does it need to be defined?  Seems like what radius means in the final equilibrated one is more important.
%BJC: This can go in supplemental
%  \begin{figure}
% 	\centering
% 	\includegraphics[width=\textwidth]{pore_radius_illustration.png}
%	\caption{The pore radius of the initial configuration is defined using the 
%        carboxylate carbon as a reference}~\label{fig:pore_radius_illustration}
%  \end{figure}

  The relative interlayer orientation was chosen based on clues from 
  diffraction data as well as the various known stacking modes of benzene 
  and substituted benzene rings: sandwiched, parallel-displaced and T-shaped
  ~\cite{sinnokrot_estimates_2002} (\Cref{fig:sandwiched,fig:pd,fig:tshaped}).
  \begin{itemize}
    \item The T-shaped configuration was ruled out based on the inconsistency of
    its $\approx$ 5 \angstrom~equilibrium stacking distance ~\cite{sinnokrot_estimates_2002}.
    \item The system's preference towards the sandwiched vs. parallel displaced 
    stacking modes will be explored.
    \item Both have reported stacking distances near the R-$\pi$ value of 3.7 \angstrom % Reference
    \item Headgroups in our sandwiched initial configuration are stacked directly
    on top of each other while stacked headgroups in the parallel displaced 
    initial configuration are offset by $180/nmon$ degrees where $nmon$ equals
    the number of monomers per layer.
    %BJC: I think the following commentary belongs elsewhere, maybe even in the discussion
    %MRS: hard to say. It's certainly a big switch from things that are relatively straightforward to things that require 
    % a fair amount of information, so I think it belongs in it's own section -- so far, you're just laying out the approach.  This is what we fix, this is what we leave as a variable.  The analysis probably belongs later.
    %BJC: Yeah, I will leave the rest for discussion
%     \item Visualization of each configuration (\Cref{fig:sandwichedlayers,fig:offsetlayers})
%     suggests entropic differences based on the way the tails are able to pack.
%     \item In the sandwiched configuration, all tails start out directly on top
%     of each other which may prevent closely stacked benzene rings.
%     \item In the offset configuration, the tails are placed in between each other 
%     which may allow layers to come together in a compact way.
%     \item This difference may explain, in part, which stacking mode is more favorable.
  \end{itemize}

  As outlined in \ref{point:monomernum} the number of monomers in each layer is unknown
  so we tested configurations constructed with a varied number of monomers per layer.
  \begin{itemize}
	\item Systems were built in the offset and parallel displaced configurations
        with 4, 5, 6, 7 and 8 monomers per layer
  \end{itemize}

  %%%%%%%%%%%% Equilibration %%%%%%%%%%%%%%

  We developed equilibration schemes to create dry and wet configurations. Both schemes 
  start with an initial configuration generated according to the previous guidelines.
  \begin{itemize}
      \item Dry equilibration scheme:
      \begin{itemize}
        %MRS2: what initial force constant, and does it matter (that can be in supplemental) 
	%BJC: I've never explored whether there is any dependence on initial force constant. It probably doesn't matter unless it starts really low
          \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
          configurations while allowing monomer tails to settle.
          \item Doing so also mitigates system dependence on initial monomer configuration.
          \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
          \item Every 50 ps, we reduce the force constants by the square root of its
          previous value, starting from 1e6 KJ mol$^-1$ nm$^-2$.
          \item Once the force constant is below 10 KJ mol$^-1$ nm$^-2$, the restraints are
          released linearly until there is no more restraining potential.
          \item The resulting unrestrained structure is allowed to equilibrate for 5 ns 
	  in the NPT ensemble with pressure controlled by the berendsen barostat.
	  \item Long, NPT equilibration simulations are run for at least 400 ns using the 
          Parrinello-Rahman barostat with a time consant of 10 ps.
      \end{itemize}
      \item Wet equilibration scheme: 
      \begin{itemize}
	  % BJC: the following three bullet points ended up not being the case since I used significantly less water
          %\item We obtained an estimate of equilibrium pore water content by solvating
          % an initial configuration with water baths above and below the membrane. 
	  %\item We ran the solvated system according to Scheme A but with a 1000 ns equilibration
          %\item Using that number we added water to the pores of an initial 
	  %configuration and equilibrated according to scheme B. 
	  \item In order to create a wet system, we solvated an initial configuration with water using gmx solvate
          \item All water molecules placed outside the pore region are removed 
	  \item Waters inside the pore region are randomly removed until the desired concentration
	  of water in the pores is reached. 
	  \item The remainder of the equilibration is the same as the dry system
      \end{itemize}
      \item In all cases, the v-rescale thermostat was used with tau-t = 0.1 % BJC: supplemental
  \end{itemize}

@@

%%%%%%%%%%%%% Crosslinking %%%%%%%%%%%%

%%%%%%%%%%%%% Equilibrium Calculations %%%%%%%%%%%%%%%

  Using equilibrated structures, we carry out various calculations to characterize the
  system. 
  \begin{itemize}
	\item We determine the point at which a system is equilibrated when the 
        distance between pores stops changing
  \end{itemize}

  To calculate the equilibrated pore spacing, we measured the distance between pore
  centers.
  \begin{itemize}
	\item Pore centers were located by averaging the coordinates of sodium ions in their
	respective pores.
	\item Statistics were generated using the bootstrapping technique (See Supplemental Information)
	% Supplemental vvvv
        \begin{itemize}
        	%MRS2: make clear sampling what?
	        \item We are interested in 5 pore-to-pore distances which should all be equal in
	        a perfect hexagonal array, however only 4 distances are independent % can visualize this in supplemental material. Will make a lot of things more clear below.
	        \item Each pore spacing has its own trajectory of spacing vs. time. Using data collected after
	        the system is equilibrated, we calculate how long it takes for the data in each of the 5
	        trajetories to become uncorrelated using pymbar.timeseries.integratedAutocorrelationTime() % reference
	        \item We break the full trajectories down into sub-trajectories based on the
	        maximum autocorrelation time of those found in the previous step.
	        \item For each bootstrap trial, we recreate an equilibrium trajectory by randomly
	        sampling pore spacings from the sub-trajectories
	        \item We get an average value for each pore spacing by finding the mean of the bootstrapped data
	        \item We calculate the overall average as the mean of all bootstrapped pore spacings
	        \item The uncertainty for each pore spacing is calculated as $\dfrac{<x> - x}{4}$ where $<x>$ is the
	        average spacing from the bootstrap trial and $x$ is the average value of one of the pore spacings.
	        \item We report the mean of these uncertainties
	        % MRS: need to deal with the fact only 4 are independent in the bootstrapping?  How did we do that?
	        % BJC: Updated
        \end{itemize}
        % Supplemental ^^^^^
  \end{itemize}

  To quantify the degree of layering and the equilibrium distance between layers
  in our system, we calculate a spatial correlation function, $g(z)$, measured
  along the z-axis (perpendicular to the membrane plane).
  \begin{itemize}
    \item To calculate $g(z)$, we binned the z component distances between
    the center of mass of each component and all others of the same pore
    over at least 50 ns of equilibrated trajectory and then normalized by the 
    average number density.
%    \item We compare the degree of layering between systems based on the
%    amplitude of the first peak in $g(z)$. We halve the difference between the
%    maximum of the first peak and the following minimum. We compare the difference
%    to the mean to get a percentage deviation from the average number density.
    \item To extract the average distance between layers we applied a discrete
    fourier transform to $g(z)$ and extracted the highest intensity frequency
  \end{itemize}

@@

  % BJC: I think this figure belongs somewhere else
  \begin{figure}
	\centering
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwiched.png}
		\caption{}\label{fig:sandwiched}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{PD.png}
		\caption{}\label{fig:pd}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Tshaped.png}
		\caption{}\label{fig:tshaped}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwichedlayers.png}
		\caption{}\label{fig:sandwichedlayers}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offsetlayers.png}
		\caption{}\label{fig:offsetlayers}
	\end{subfigure}
	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
	3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart. 
	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
	configuration }\label{fig:stacking}
  \end{figure}

  We explored the pore composition by measuring the average number densities of
  various monomer components with respect to the pore centers.
  \begin{itemize}
	\item The centers of the pores were located using the same method to
        calculate the equilibrium pore spacing
        \item We looked at the average number density of sodium ions, aromatic
	rings and carbon atoms making up the monomer tails 
	\item The radial distance from the pore center of all atoms in each group
        are binned then normalized by area 
	% Maybe write an equation here? It's hard to say precisely how I did it in words without it sounding confusing 
  \end{itemize}
